\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-23 root.tex
minor edits in trajectory section

The path manager is implemented as a discrete state machine, depicted in Fig. \ref{fig:st}.
Each of the states is described below.

@@

Prescribed initial and end conditions for position, speed, and acceleration must be honored.
All planning is longitudinal; that is, speed is the primary focus, and we assume that the control subsystem will ensure that the vehicle follows the prescribed path.
This means that the desired trajectory plan may be mapped into one dimension using curvilinear coordinates to significantly simplify the solution.
We show how two dimensional constraints (specifically cornering speeds for this work) are expressed in one dimension to guide planning.

@@

The task of Trajectory Planning is to take a one dimensional set of waypoints from the Path Manager, and compute a series of constant jerk intervals for motion along the length of the path.
This trajectory must be time optimal yet still fall within constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

@@

Our approach to fitting appropriate jerk profiles to complex sub-paths is to further break each sub-path into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ for must be defined for each segment.
A sub-path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_{k_s}$, $\mathbf{a}_{m,k_s}$, and $\mathbf{j}_{m,k_s}$ where $k_S = 1 ... N_s$ and can be solved individually in sequence.

@@

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k_p}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_{k_p}}$ for $k_p = 1, ..., N_p$, where $N_p$ is the number of waypoints in the sub-path.
The value $\kappa_{k_P}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,k_p}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.

@@

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{SegmentBoundarySpeeds}{$v_m$}
      \State $\mathbf{v}_p \gets \mathbf{v}_m$ \Comment{Initialize targets as ceilings}
      \State $\mathbf{v}_{p,0} \gets v_i$ \Comment{Set starting speed to current}
      \State $\mathbf{v}_p = [\mathbf{v}_p, 0]$ \Comment{Add final speed of 0}
      \For{$i = 1, ..., N_s-1$}
        \If{$v_{m,i+1} > v_{m,i}$}
          \State $v_{p,i+1} \gets v_{m,i+1}$
        \Else
          \State $v_{p,i+1} \gets v_{m,i}$
        \EndIf
      \EndFor
    \EndProcedure
  \end{algorithmic}
  \caption{
    Algorithm to set speed boundary conditions for interior segments.
    Having consolidated the waypoints in to a set of path segments, the maximum allowable speed for each segment, $v_{m,i}$ is known.
    This algorithm uses the set of $\mathbf{v_{m}}$ for all segments to choose the highest allowable start and end speeds for each path segment.
  }
\label{alg:segmentspeedboundaryconditions}
\end{figure}

@@

There are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose to define 4 other basic profiles to cover all feasible values in $\mathbf{b}$., and our algorithm judiciously chooses the appropriate profile.
The other profiles are explained below.

All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, traveling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that traveling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for $[\Delta t_1, ..., \Delta t_M]$, given $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$, a symbolic solver was used.

@@

\begin{figure}[thpb]
  \centering
  \begin{tabular}{cc}
  \subfigure[6-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/6phase_v(s).png}
  \label{fig:6phaseprofile}
  } &
  \subfigure[4-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4phase_v(s).png}
  \label{fig:4phaseprofile}
  } \\
  \subfigure[Reversed 4-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \label{fig:4rphaseprofile}
  } &
  \subfigure[3-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/3phase_v(s).png}
  \label{fig:3phaseprofile}
  }
  \end{tabular}
  \caption{6, 4, Reversed 4 and 3-phase profiles, displayed as speed vs. position along path}

@@

The procedure for planning NORMAL mode trajectories is separate from that used to compute RSTOP trajectories.
A 3-phase profile will be used, with end conditions $v_f=0, a_f=0$ and initial conditions set to the current state of the navigation filter.
While it would seem that the segment solving procedure described in Sec. \ref{sec:3phase} could be applied to reactive stopping, this is not the case.
As was mentioned previously, only one of $[L, v_f]$ may be rigidly enforced for a 3-phase profile, but not both, since no closed-form solution exists for that case.
Normal planning enforces $L$ to avoid skewing segment boundaries within each subpath.
However, reactive stopping requires that $v_f$ be enforced, and that we solve for $L$.
Reformulating a new 3-phase jerk profile accordingly is a simple matter for a symbolic solver.
%%% This is the brief way of wording the preceding three sentences.
% The trajectory planner uses total distance as parameter, and is not suitable for our purpose as the end speed constraints are not met. So we reformulate and replace $L$ with $v_f$ as the hard constraint.

>>>>

The Path Manager is implemented as a discrete state machine, depicted in Fig. \ref{fig:st}.
Each of the states is described below.

@@

Prescribed initial and end conditions for position, speed, and acceleration must be honored.
All planning is longitudinal; that is, speed profile generation is the primary focus, and we assume that the control subsystem will ensure that the vehicle follows the prescribed path.
This means that the desired trajectory plan may be mapped onto one dimension using curvilinear coordinates to significantly simplify the solution.
We show how two dimensional constraints (specifically cornering speeds for this work) are expressed in one dimension to guide planning.

@@

The task of Trajectory Planning is to take a 1D set of waypoints from the Path Manager, and compute a series of constant jerk intervals for motion along the length of the path.
The resulting trajectory must be time optimal and satisfy all the constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

@@

In this section we describe our approach to fitting appropriate jerk profiles to complex sub-paths. 
We first break each sub-path into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ must be defined for each segment.
A sub-path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_{k_s}$, $\mathbf{a}_{m,k_s}$, and $\mathbf{j}_{m,k_s}$ where $k_S = 1 ... N_s$ and can be solved individually in sequence.

@@

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation \textbf{ RG: using centrifugal  force relationship ????} $v_{m,k_p}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_{k_p}}$ for $k_p = 1, ..., N_p$, where $N_p$ is the number of waypoints in the sub-path.
The value $\kappa_{k_P}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,k_p}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.

@@

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{SegmentBoundarySpeeds}{$v_m$}
      \State $\mathbf{v}_p \gets \mathbf{v}_m$ \Comment{Initialize targets as ceilings}
      \State $\mathbf{v}_{p,0} \gets v_i$ \Comment{Set starting speed to current}
      \State $\mathbf{v}_p = [\mathbf{v}_p, 0]$ \Comment{Add final speed of 0}
      \For{$i = 1, ..., N_s-1$}
        \If{$v_{m,i+1} > v_{m,i}$}
          \State $v_{p,i+1} \gets v_{m,i+1}$
        \Else
          \State $v_{p,i+1} \gets v_{m,i}$
        \EndIf
      \EndFor
    \EndProcedure
  \end{algorithmic}
  \caption{
    Algorithm to set speed boundary conditions for interior segments.
    Having consolidated the waypoints into a set of path segments, the maximum allowable speed for each segment, $v_{m,i}$ is known.
    This algorithm uses the set of $\mathbf{v_{m}}$ for all segments to choose the highest allowable start and end speeds for each path segment.
  }
\label{alg:segmentspeedboundaryconditions}
\end{figure}

@@

We propose to define 4 other basic profiles to cover all feasible values in $\mathbf{b}$, and our algorithm judiciously chooses the appropriate profile. These 4 cases cover cases in which the 7-phase solution fails. For instance, if $L$ is too short or $v_m$ is too high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
The other profiles are explained below.

All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, traveling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that traveling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for $[\Delta t_1, ..., \Delta t_M]$, given $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$, a symbolic solver was used \textbf{RG: can specify solver name???} .

@@

\begin{figure}[thpb]
  \centering
  \begin{tabular}{cc}
  \subfigure[6-phase profile] {
  \includegraphics[width=0.43\columnwidth]{graphics/6phase_v(s).png}
  \label{fig:6phaseprofile}
  } &
  \subfigure[4-phase profile] {
  \includegraphics[width=0.43\columnwidth]{graphics/4phase_v(s).png}
  \label{fig:4phaseprofile}
  } \\
  \subfigure[Reversed 4-phase profile] {
  \includegraphics[width=0.43\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \label{fig:4rphaseprofile}
  } &
  \subfigure[3-phase profile] {
  \includegraphics[width=0.43\columnwidth]{graphics/3phase_v(s).png}
  \label{fig:3phaseprofile}
  }
  \end{tabular}
  \caption{6, 4, Reversed 4 and 3-phase profiles, displayed as speed vs. position along path.}

@@

The procedure for planning NORMAL mode trajectories is separate from that used to compute RSTOP trajectories.
A 3-phase profile is used, with end conditions $v_f=0, a_f=0$ and initial conditions set to the current state of the navigation filter.
While it would seem that the segment solving procedure described in Sec. \ref{sec:3phase} could be applied to reactive stopping, this is not the case.
As was mentioned previously, only one of $[L, v_f]$ may be rigidly enforced for a 3-phase profile, but not both, since no closed-form solution exists for that case.
Normal planning enforces $L$ to avoid skewing segment boundaries within each subpath.
However, reactive stopping requires that $v_f$ be enforced, and that we solve for $L$.
Reformulating a new 3-phase jerk profile accordingly is a simple matter for a symbolic solver.
%%% This is the brief way of wording the preceding three sentences.
% The trajectory planner uses total distance as parameter, and is not suitable for our purpose as the end speed constraints are not met. So we reformulate and replace $L$ with $v_f$ as the hard constraint.
